Avoiding tipping points in fisheries management through Gaussian Process Dynamic Programming

### 2014-12-05 manuscripts/manuscript.Rmd
add explicit note about archived code, data, etc

We first describe the requirements of dynamic optimization for the
management of human intervention in natural resource systems. After that
we describe three parametric models for population dynamics and the Gaussian
Process (GP)[^1] description of population dynamics.

[^1]: We abbreviate Gaussian Process as GP, which refers to 
the statistical model we use to approximate the population dynamics, and we use the
term Gaussian Process Dynamic Programming [GPDP,], to refer to the _use_ of a
GP as the underlying process model when solving a Dynamic Programming equation.
Hence we will refer to the models as: GP, Ricker, Allen, etc, and the novel method we put forward here as GPDP.

>>>>

We first describe the requirements of dynamic optimization for the
management of human intervention in natural resource systems. After that
we describe three parametric models for population dynamics and the Gaussian
Process (GP)[^1] description of population dynamics. All computer code
used here has been embedded in the manuscript sources (see @Xie_2013),
and an implementation of the GPDP approach is provided as an accompanying R
package.  Source code, R package and the CSV data files corresponding each
figure are archived in the supplement [@Boettiger_2014].

[^1]: We abbreviate Gaussian Process as GP, which refers to 
the statistical model we use to approximate the population dynamics, and we use the
term Gaussian Process Dynamic Programming (GPDP), to refer to the _use_ of a
GP as the underlying process model when solving a Dynamic Programming equation.
Hence we will refer to the models as: GP, Ricker, Allen, etc, and the novel method we put forward here as GPDP.

### 2014-12-05 manuscripts/manuscript.tex
add explicit note about archived code, data, etc

We first describe the requirements of dynamic optimization for the
management of human intervention in natural resource systems. After that
we describe three parametric models for population dynamics and the
Gaussian Process (GP)\footnote{We abbreviate Gaussian Process as GP,
  which refers to the statistical model we use to approximate the
  population dynamics, and we use the term Gaussian Process Dynamic
  Programming {[}GPDP,{]}, to refer to the \emph{use} of a GP as the
  underlying process model when solving a Dynamic Programming equation.
  Hence we will refer to the models as: GP, Ricker, Allen, etc, and the
  novel method we put forward here as GPDP.} description of population
dynamics.

@@

@@

>>>>

We first describe the requirements of dynamic optimization for the
management of human intervention in natural resource systems. After that
we describe three parametric models for population dynamics and the
Gaussian Process (GP)\footnote{We abbreviate Gaussian Process as GP,
  which refers to the statistical model we use to approximate the
  population dynamics, and we use the term Gaussian Process Dynamic
  Programming (GPDP), to refer to the \emph{use} of a GP as the
  underlying process model when solving a Dynamic Programming equation.
  Hence we will refer to the models as: GP, Ricker, Allen, etc, and the
  novel method we put forward here as GPDP.} description of population
dynamics. All computer code used here has been embedded in the
manuscript sources (see Xie (2013)), and an implementation of the GPDP
approach is provided as an accompanying R package. Source code, R
package and the CSV data files corresponding each figure are archived in
the supplement (Munch; 2014).

@@

Munch; C. B. M. M. S. 2014. nonparametric-bayes v0.1.0. ZENODO.
\url{http://dx.doi.org/10.5281/zenodo.12669}.

@@

Xie, Y. 2013. Dynamic documents with R and knitr. Chapman; Hall/CRCBoca
Raton, Florida.
